Empirical Analysis of the Role of Energy in Economic Growth

### 2013-01-18 EconGrowth.Rnw
Adjusted number of decimal places in tables.

@@

# Now create the data for a table.
dataCD <- rbind(lowerCD, estCD, upperCD); dataCD
colnames(dataCD)  <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
tableCD <- xtable(dataCD, caption="U.S. Cobb-Douglas, 1980-2011", digit = c(4))
@

<<CD Results, results='asis'>>=
print(tableCD, caption.placement="top")
# According to http://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf, Section 3.1, I should 
# be able to use the "sanitize.text.function" parameter to allow markup in column headers. But this next
# line is not working at the present time. --MKH, 18 Jan 2012.
# print(tableCD, sanitize.text.function = function(x){x})
@

@@

# Now create the data for a table.
dataCDq <- rbind(lowerCDq, estCDq, upperCDq); dataCDq
colnames(dataCDq)  <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
tableCDq <- xtable(dataCDq, caption="U.S. 1980-2011.", digit = c(4))

dataAll <- rbind(estCD, estCDq); dataAll
tableAll <- xtable(dataAll, caption="U.S. 1980-2011, All Models.", digit = c(4))
@

>>>>

<<testing>>=
mat <- round(matrix(c(0.9, 0.89, 200, 0.045, 2.0), c(1, 5)), 4)
rownames(mat) <- "$y_{t-1}$"
# colnames(mat) <- c("$R^2$", "$\\bar{R}^2$", "F-stat", "S.E.E", "DW")
colnames(mat) <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$", "DW")
mat <- xtable(mat)
@

<<Test Print Sanitized Table, results='asis'>>=
print(mat, sanitize.text.function = function(x){x})
@

@@

# Now create the data for a table.
dataCD <- rbind(lowerCD, estCD, upperCD); dataCD
colnames(dataCD) <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
tableCD <- xtable(dataCD, caption="U.S. Cobb-Douglas, 1980-2011", digit = c(4, 4, 2, 2, 1))
@

<<CD Results, results='asis'>>=
print(tableCD, caption.placement="top")
# According to http://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf, Section 3.1, I should 
# be able to use the "sanitize.text.function" parameter to allow markup in column headers. But this next
# line is not working at the present time. --MKH, 18 Jan 2012.
# print(tableCD, caption.placement="top", sanitize.text.function = function(x){x})
@

@@

# Now create the data for a table.
dataCDq <- rbind(lowerCDq, estCDq, upperCDq); dataCDq
colnames(dataCDq)  <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
tableCDq <- xtable(dataCDq, caption="U.S. 1980-2011.", digit = c(4, 4, 2, 2, 3))

dataAll <- rbind(estCD, estCDq); dataAll
tableAll <- xtable(dataAll, caption="U.S. 1980-2011, All Models.", digit = c(4, 4, 2, 2, 3))
@
